\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning on Unsecured Trajectories

### 2023-10-30 paper.tex
update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
This paper addresses the critical issue of security in multi-robot systems (MRS) when facing threats from adversaries attempting to compromise the robots' control. Such compromises could lead to unauthorized access to forbidden areas, potentially causing harm or disrupting the mission. To tackle this problem, we propose a novel multi-robot planning algorithm that leverages mutual observations between robots as an additional security measure. Our approach guarantees that even in the face of adversarial movement by attackers, compromised robots cannot reach forbidden regions without missing scheduled co-observations. 
We achieve this by introducing \emph{reachability} constraints into continuous trajectory planning algorithm. These constraints ensure an empty intersection between the sets of locations that the agents could potentially reach and the forbidden regions. 
\rtron{The reachability constraint is implemented with ellipsoidal over-approximation; this allows to quickly check intersection and compute gradients.}
Furthermore, to enhance system resilience and feasibility of the planning problem, we introduce the concept of \emph{sub-teams}, where multiple robots form cohesive units along each route, replacing individual robot assignments. This redundancy enables robots to deviate from their assigned sub-teams and join others to perform cross-trajectory co-observations, thereby securing multiple trajectories simultaneously. To efficiently plan cross-trajectory co-observations that maintain security against plan-deviation attacks, we formulate the multi-flow problem on unsecured MRS trajectories. 
\rtron{This second part fixes the feasiblity problems of the first one, and uses the same reacheability constraints to build inter-team trajectories.}
We demonstrate the effectiveness and robustness of our proposed algorithm, which significantly strengthens the security of multi-robot systems in the face of adversarial threats.
\end{abstract}

\section{Introduction}\label{sec:introduction}
Multi-robot systems (MRS) have witnessed increasing adoption in diverse fields, such as warehouse organization, surveillance, forest fire monitoring, and precision agriculture, owing to their capacity for complex task execution through cooperation and coordination \cite{pajares2015overview, julian2012distributed}. The use of MRS offers numerous advantages, but it also introduces new cybersecurity challenges, including unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}. Given their distributed nature and reliance on network communication, MRS are particularly vulnerable to cyber threats. In this paper, we address the specific scenario where attackers compromise robots and direct them to restricted regions, potentially leading to the exploitation of confidential information, physical property damages, or even human injuries \cite{forrest_2017}. We refer to these restricted regions as \emph{forbidden regions}, which might contain security-sensitive equipment or human workers.

These deliberate deviations, termed \emph{plan-deviation attacks}, have been previously identified and tackled in the literature \cite{wardega2019resilience} \zyang{add most recent articles}. The work of \cite{wardega2019resilience} provide exact solution for grid-world configuration. Using the onboard sensing capabilities, robots can perform inter-robot observations as an additional security measure. Each robot' self-report includes not only its own status, but also additional observations of other robots' status. For example, robot $i$'s self-report may include its observation of robot $j$, ``$i$ report its arrival at $v$ and $i$ observes $j$ at location $w$''. Similarly, robot $j$ also reports its observations of robot $i$ to the CE. This solution provides paths with an observation schedule such that any attempts by a compromised robot to violate the safety constraints would necessarily break the observation plan and be detected.

@@

\subsection{Co-observation performance}
Notice that problem \eqref{eq:flow-coverage-problem} is guaranteed to have a solution for $\cK=N_{p}$ where all $\cK$ robots follows the reference trajectory ($f^{k}_{ij}=1, \forall \cI_{v_{i}}=\cI_{v_{j}}=k$).  Additionally, for a fixed number of robots $\cK \geq N_{p}$, it is possible to have a subset of flows $F_{e} \in F$ that is empty, i.e. $f_{ij}=0, \forall (v_{i},v_{j})\in E$, $f\in F_{e}$, these flow will not increase the cost and will not have any impact on the solution.  
The trade-off between the number of surveillance robots and security performance is crucial, with an increase in robots generally enhancing security via cross-trajectory co-observations. However, this improvement can be offset by heightened complexity and coordination challenges. To balance these aspects, the penalty parameter $\rho$ in the cost function \ref{eq:flow-cost} is optimized, achieving an equilibrium between security enhancement and operational efficiency. An iterative approach with $\cK=1$ gradually increases until $F$ contains an empty flow, indicating the point where further robot additions do not improve performance. To control unbounded growth, $\rho$ regulates the second term for a single flow in \eqref{eq:flow-cost} $ \rho \sum_{(ij)\in E} w_{ij} f^k_{ij}$ is always smaller than $1$.

@@

The flows derived from the solution of the optimization problem \eqref{eq:flow-coverage-problem} are highlighted in the graph. The planning result in the workspace is shown in \ref{fig:workspace-3-flow} as dash-dotted arrows with the same color used for each flow in \ref{fig:security-graph-3-flow}. Notice that flows represent the robot co-observation plan instead of actual robots, such that the red flow, for example, shows that the sub-team 2 is expecting a robot from sub-team 1, departing at $t=0$ and arriving at $t=10$, and needs to send a robot (not necessarily the same one received from sub-team 1) to sub-team 3, departing at $t=67$ and arriving at $t=79$. This plan is not ideal in terms of our security criteria since co-observations happens between the same pair of surveillance robot and sub-team for the majority of the time with only three cross-trajectory edges that are covered.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
This paper addresses the critical issue of security in multi-robot systems (MRS) when facing threats from adversaries attempting to compromise the robots' control which could lead to unauthorized access to forbidden areas, potentially causing harm or disrupting the mission. To tackle this problem, we propose a novel multi-robot planning algorithm that leverages mutual observations between robots, and introducing  \emph{reachability} constraints as additional security measures. By enforcing an empty intersection between the locations that the agents could potentially reach (using reachability constraint) and the forbidden regions, we provide guarantees that even in the face of adversarial movement by attackers, compromised robots cannot reach forbidden regions without missing scheduled co-observations. The reachability constraint is implemented with ellipsoidal over-approximation; this allows to quickly check intersection and compute gradients.

Furthermore, to further enhance system resilience and address the feasibility challenges encountered in the initial stage, we introduce the concept of \emph{sub-teams}, where multiple robots form cohesive units along each route, replacing individual robot assignments. This allows redundant robots to deviate for co-observations across different sub-teams, ensuring the security of multiple trajectories without the need for trajectory modifications of the entire sub-team. To plan cross-trajectory co-observations that maintain security against plan-deviation attacks, we formulate the multi-flow problem on unsecured MRS trajectories,

We demonstrate the effectiveness and robustness of our proposed algorithm, which significantly strengthens the security of multi-robot systems in the face of adversarial threats.
\end{abstract}

\section{Introduction}\label{sec:introduction}
Multi-robot systems (MRS) have witnessed increasing adoption in diverse fields, such as warehouse organization, surveillance, forest fire monitoring, and precision agriculture, owing to their capacity for complex task execution through cooperation and coordination \cite{pajares2015overview, julian2012distributed}. The use of MRS offers numerous advantages, but given their distributed nature and reliance on network communication, MRS are particularly vulnerable to cyber threats which introduces new cybersecurity challenges (e.g. unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}). In this paper, we address the specific scenario where attackers compromise robots and direct them to restricted regions, potentially leading to the exploitation of confidential information, physical property damages, or even human injuries \cite{forrest_2017}. We refer to these restricted regions as \emph{forbidden regions}, which might contain security-sensitive equipment or human workers.

These deliberate deviations, termed \emph{plan-deviation attacks}, have been previously identified and tackled in the literature \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola, yang2021multi, yang2020multi} \zyang{add most recent articles}. These works initial solution for grid-world configuration, where robots is tasked perform inter-robot observations (usilizing the onboard sensing capabilities) as an additional security measure. Each robot' self-report includes not only its own status, but also additional observations of other robots' status. For example, robot $i$'s self-report may include its observation of robot $j$, ``$i$ report its arrival at $v$ and $i$ observes $j$ at location $w$''. Similarly, robot $j$ also reports its observations of robot $i$ to the CE \cite{wardega2019resilience}. This solution provides paths with an observation schedule such that any attempts by a compromised robot to violate the safety constraints would necessarily break the observation plan and be detected.

@@

\subsection{Co-observation performance}
Notice that problem \eqref{eq:flow-coverage-problem} is guaranteed to have a solution for $\cK=N_{p}$ where all $\cK$ robots follows the reference trajectory ($f^{k}_{ij}=1, \forall \cI_{v_{i}}=\cI_{v_{j}}=k$).  Additionally, for a fixed number of robots $\cK \geq N_{p}$, it is possible to have a subset of flows $F_{e} \in F$ that is empty, i.e. $f_{ij}=0, \forall (v_{i},v_{j})\in E$, $f\in F_{e}$, these flow will not increase the cost and will not have any impact on the solution.

The trade-off between the number of surveillance robots and security performance is crucial, with an increase in robots generally enhancing security via cross-trajectory co-observations. However, this improvement can be offset by heightened complexity and coordination challenges. To balance these aspects, the penalty parameter $\rho$ in the cost function \ref{eq:flow-cost} is optimized, achieving an equilibrium between security enhancement and operational efficiency. An iterative approach with $\cK=1$ gradually increases until $F$ contains an empty flow, indicating the point where further robot additions do not improve performance. To control unbounded growth, $\rho$ regulates the second term for a single flow in \eqref{eq:flow-cost} $ \rho \sum_{(ij)\in E} w_{ij} f^k_{ij}$ is always smaller than $1$.

@@

The flows derived from the solution of the optimization problem \eqref{eq:flow-coverage-problem} are highlighted in the graph. The planning result in the workspace is shown in \ref{fig:workspace-3-flow} as dash-dotted arrows with the same color used for each flow in \ref{fig:security-graph-3-flow}.  This plan is not ideal in terms of our security criteria since co-observations happens between the same pair of surveillance robot and sub-team for the majority of the time with only three cross-trajectory edges that are covered.
